### 2023-12-15 main.tex
Appendix A fixed

\appendix 
\section*{Appendix}
\section{Interpretation of $\Psi^{'}$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp} 
We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau}= (N,\ldots,N)$. We show here that for this particular configuration
$\Psi^{'}(N,\ldots,N) =1$. Indeed, for any $\bm{\tau}\in \Omega^{'}$ we have that 
\begin{align}
	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle\dt
\end{align} 
We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$. More explicitly, this dual configuration is given by
\begin{equation}
	\begin{cases}
		\xi_{a}^{x}(\bm{\tau})= \delta_{\tau_{x},a}\qquad \forall a\in \{1,\ldots N\}\quad \forall x\in \{1,\ldots,L\}\\
		\xi_{N}^{0}(\bm{\tau})=\xi_{N}^{L+1}(\bm{\tau})=1
	\end{cases}\dt
\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and we have
\begin{align}\label{useful-InInterpretation}
	\Psi^{'}(\bm{\tau})=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle\dt
\end{align}
We observe that for any $x\in \{1,\ldots,L\}$
\begin{equation}
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{(1-\delta_{\tau_{x},N})}%=\begin{cases}
		%	\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		%	1\qquad  &\text{if}\quad \tau_{x}= N
		%	\end{cases}
		\dt
\end{equation}
Indeed, we have that 
\begin{equation}
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}
		\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		1\qquad  &\text{if}\quad \tau_{x}= N
	\end{cases}\dt
\end{equation}
Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation~\ref{useful-InInterpretation}, we obtain 
\begin{equation}%\label{interpretation-PsiP}
	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
\end{equation} 
This last equation completes and generalizes \eqref{corr-psi1} by showing that $\Psi^{'}(N,\ldots,N) =1$.

Equivalently, we can interpret the components of $\Psi'(\bm{\tau})$ as follows.
Let $\ell$ be the number of occupied sites in the configuration $\bm{\tau}$, i.e.  $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$. We denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle of any (non-empty) type is present. Finally, we call 
\begin{equation}
	\Omega_{\ell}^{'}(\bm{\tau}):=\left\{\bm{\sigma}\in \Omega^{'}\;:\; \sigma_{x_{1}}=\tau_{x_{1}},\ldots,\sigma_{x_{\ell}}=\tau_{x_{\ell}}\right\}\dt
\end{equation} 
Observe that, if $\ell=0$ then $\Omega_{\ell}^{'}(\bm{\tau})$ does coincide with the whole state space $\Omega^{'}$, while, if $\ell=L$ then $\Omega_{\ell}^{'}(\bm{\tau})$ reduces to the configuration $\bm{\tau}$. Denoting the marginal on $\ell$ sites of the steady state distribution by 
\begin{equation}
	\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})
\end{equation}
we have that 
\begin{align}
	\Psi^{'}(\bm{\tau})=&\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]=\mathbb{E}\left[\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=\tau_{x_{k}}\}}\right]=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})\dt
\end{align} 
It follows that $\Psi^{'}(\bm{\tau})$ is the marginal on $\ell$ sites $x_{1},\ldots,x_{\ell}$ of the non-equilibrium steady state distribution. In particular, when the configuration $\bm{\tau}$ has $\ell$ particles, $\Psi^{'}(\bm{\tau})$ does coincide with the $\ell$-point correlation function. 
%As a consequence, all the marginals of $\mu$ can be found using the absorption probabilities by equation \eqref{exactCorrelations}.

>>>>

\appendix 
\section*{Appendix}
\section{Interpretation of $\Psi^{'}$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp} 
We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau}= (N,\ldots,N)$. We show here that for this particular configuration
$\Psi^{'}(N,\ldots,N) =1$. Indeed, for any $\bm{\tau}\in \Omega^{'}$ we have that 
\begin{align}
	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle\dt
\end{align} 
{\color{blue}We introduce the dual configuration constructed by attaching two extra-sites (without any particle) to the vector $\bm{\tau}$, transforming its dimension from $L$ to $L+2$. We denote it by $\bm{\xi}(\bm{\tau})=(0,\tau_{1},\ldots,\tau_{L},0)$, where we wrote $0$ in the two extra-sites to indicate that no dual particles are present there.}  More explicitly, this dual configuration is given by
\begin{equation}
	\begin{cases}
		\xi_{A}^{x}(\bm{\tau})= \delta_{\tau_{x},A}\qquad \forall A\in \{1,\ldots N\}\quad \forall x\in \{1,\ldots,L\}\\
		\xi_{1}^{0}(\bm{\tau})=\ldots=\xi_{N-1}^{0}(\bm{\tau})=0\\
		\xi_{1}^{L+1}(\bm{\tau})=\ldots=\xi_{N-1}^{L+1}(\bm{\tau})=0
	\end{cases}\dt
\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and, {\color{blue} since no dual particles are present in the extra-sites $0$ and $L+1$}, we have
\begin{align}\label{useful-InInterpretation}
	\Psi^{'}(\bm{\tau})=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle\dt
\end{align}
We observe that for any $x\in \{1,\ldots,L\}$
\begin{equation}
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{(1-\delta_{\tau_{x},N})}%=\begin{cases}
		%	\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		%	1\qquad  &\text{if}\quad \tau_{x}= N
		%	\end{cases}
		\dt
\end{equation}
Indeed, we have that 
\begin{equation}
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}
		\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		1\qquad  &\text{if}\quad \tau_{x}= N
	\end{cases}\dt
\end{equation}
Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation~\ref{useful-InInterpretation}, we obtain 
\begin{equation}%\label{interpretation-PsiP}
	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
\end{equation} 
This last equation completes and generalizes \eqref{corr-psi1} by showing that $\Psi^{'}(N,\ldots,N) =1$.

Equivalently, we can interpret the components of $\Psi'(\bm{\tau})$ as follows.
Let $\ell$ be the number of sites {\color{blue}occupied by a particle} in the configuration $\bm{\tau}$, i.e.  $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$. We denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle of any species is present. Finally, we call 
\begin{equation}
	\Omega_{\ell}^{'}(\bm{\tau}):=\left\{\bm{\sigma}\in \Omega^{'}\;:\; \sigma_{x_{1}}=\tau_{x_{1}},\ldots,\sigma_{x_{\ell}}=\tau_{x_{\ell}}\right\}\dt
\end{equation} 
Observe that, if $\ell=0$ then $\Omega_{\ell}^{'}(\bm{\tau})$ does coincide with the whole state space $\Omega^{'}$, while, if $\ell=L$ then $\Omega_{\ell}^{'}(\bm{\tau})$ reduces to the configuration $\bm{\tau}$. Denoting the marginal on $\ell$ sites of the steady state distribution by 
\begin{equation}
	\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})
\end{equation}
we have that 
\begin{align}
	\Psi^{'}(\bm{\tau})=&\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]=\mathbb{E}\left[\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=\tau_{x_{k}}\}}\right]=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})\dt
\end{align} 
It follows that $\Psi^{'}(\bm{\tau})$ is the marginal on $\ell$ sites $x_{1},\ldots,x_{\ell}$ of the non-equilibrium steady state distribution. In particular, when the configuration $\bm{\tau}$ has $\ell$ particles, $\Psi^{'}(\bm{\tau})$ does coincide with the $\ell$-point correlation function. 
%As a consequence, all the marginals of $\mu$ can be found using the absorption probabilities by equation \eqref{exactCorrelations}.
